---
title: "nathan's rough draft"
author: "nathan"
date: "7/16/2021"
output: html_document
---

```{r setup, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
library(sf)
library(cwi)
library(viridis)
# run this line if you want to use some setup code i wrote up
source(here::here("src", "static", "setup.R"))
```

First is data import! I'm using the `here::here()` function to handle file paths consistently/reliably in Rmarkdown. I'm also making one edit to Camille's `new_haven_sf` dataset from the `cwi` package, to fit the data Annie Harper provided to us. 

```{r, message = FALSE}
dta <- here("data","debt_counts_Neighborhood_all_aggr.csv") %>% 
  read_csv()
colname_conversions <- here("data", "colname_conversions.csv") %>% 
  read_csv()

new_haven_sf <- mutate(new_haven_sf, 
                       name = ifelse(name == "Wooster Sq/ Mill River",
                                             "Wooster Square",
                                             as.character(name)))
```

Second is data cleanup. I'm planning to iterate through my columns in a loop, so I'm "pivoting" the data so that the columns become copied into rows. This way it can be "split" row-wise, and each item in the resulting split can be passed through the loop. I also tack on some name revisions from a spreadsheet I hand-coded for the column names, and I attach geometries so that these data can be mapped. 

```{r}
dta <- dta %>% 
  select(neighborhood:avg_unsecured_share_all) %>% 
  left_join(new_haven_sf, c("neighborhood" = "name")) %>% 
  pivot_longer(avg_total_debts_all:avg_unsecured_share_all) %>%  
  left_join(colname_conversions, by = "name") %>% 
  st_as_sf() %>% 
  group_split(name)

```

And lastly there's actually writing the loop and iterating through it. I'm using `map` from the `purrr` library, which is the community-preferred way of looping. The `map` function lets you define a function outside of the actual loop (it could also be inside, your choice). This encouraged flexibility is an alternative to the structure of the `for` loop, and the refresh of scope and state also can make code more prone to catching errors before they mess you up. The `map` function lastly also fits well in the dplyr pipe (the `%>%` symbol). 

I just create one simple choropleth and one simple bar chart for each variable. 

```{r, results = 'hide'}
process_group <- function(dta_group){
  name <- unique(dta_group$name)
  replacement <- unique(dta_group$replacement)
  
  #a very basic map
  ggplot(dta_group) +
    geom_sf(aes(fill = value)) + 
    labs(title = replacement, fill = NULL) + 
    scale_fill_viridis(option = "magma") + 
    theme_map() + 
    theme(legend.key.height = unit(2, "lines")) + 
    ggsave(here("plots", "nathan_rough", "maps", paste0(name, ".png")),
           height = 7, width = 7)
  
  # a very basic bar chart
  dta_group %>% 
    drop_na(value) %>% 
    mutate(highlight = rank(value, "first"),
           highlight = case_when(highlight > max(highlight) - 3 ~ T, 
                                 highlight < min(highlight) + 3 ~ F,
                                 T ~ NA),
           neighborhood = fct_reorder(neighborhood, value) %>% fct_drop()) %>% 
    drop_na(highlight) %>% 
    ggplot() + 
    geom_bar(aes(x = neighborhood, y = value, fill = highlight),
             stat = "identity") + 
    scale_fill_manual(values = c("#33658A", "#F6AE2D")) + 
    labs(title = replacement, 
         y = NULL, x = "Neighborhood",
         caption = "Top three and bottom three neighborhoods for the metric are shown.") + 
    theme_bw(base_family = "Lato") + 
    theme(legend.position = "none",
          plot.background = element_rect(fill = NA)) + 
    ggsave(here("plots", "nathan_rough", "bars", paste0(name, ".png")),
           height = 7, width = 7)
  return(invisible(NULL))
}

dta %>% 
  map(process_group)
```

Lots of things to revise!

- Color palettes
- Theming (font sizes/text hierarchy)
- Specific trends we want to highlight
- Some bar charts have four, some have three. Why? 

